TODO

### 2025-01-07 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
add diagram and do work on incorporating intro

TODO introduction

@@

## Materials
For the target stimuli, we used four of the ten tangram images from @leung, chosen based on visual dissimilarity. We coded the matching game using Empirica and hosted it on a lab server (CITATION). We then accessed the game on the web on tablets that were locked in a kiosk mode so children could not navigate to other websites or applications during the game.

## Procedure
Once a pair of children agreed to play the game, a research assistant took them to a quiet testing room where the game was explained to them. Children were introduced to a stuffed animal "Smurfy" who wanted to play a matching game. Children sat across a table from each other, each with a tablet in front of them. On each trial, one child saw two images, one of them in a black box, and was asked to "say what they saw" in the black box so their partner (and Smurfy) could tap the corresponding image. The guesser saw the same two images (in a randomized order), but with neither boxed. Upon tapping an image, both children received feedback in form of a smiley or frowny face and an audible sound. After each trial, children's roles switched. Children passed Smurfy back and forth to help them keep track of whether they were the "guesser" or "teller" on a given trial.

Children completed two warm-up trials with black and white images of familiar shapes, followed by 3 blocks of the 4 targets. Targets were randomly paired with another of the critical images as the foil.

@@

TODO DIAGRAM OF EXPERIMENT + Picture of children playing the game as top bar

```{r interface, fig.env = "figure*", fig.pos = "t!", fig.width=6, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "TODO \\label{game}", cache=FALSE}
```

@@

## Materials
The same 4 critical images were used as in experiment 1, although this time, children saw these images 4 times. In response to some children struggling with the abrupt switch from nameable to non-nameable shapes, we introduced more practice trials for experiment 2. We used a total of 4 practice trials, designed to transition from easily recognizable shapes to slightly blockier black and wide shapes to smooth the transition to the critical trials. 
## Procedure
The procedure was much the same. We added an initial "bubble popping" exercise to give children practice with how to tap the tablet appropriately (this was an issue for some children in the first experiment). The smurfy puppet was swapped out for a more attractive smurfy stuffed animal. The experimental script was fully written out so children all recieved the same instructions. To prevent experimenter's influencing children's descriptions or understanding of descriptions, we wrote up contingency statements that the experimenter could use to prompt children who were not giving descriptions or making selections. TODO link to materials for where the script is.

>>>>

<!-- intro --> 
Learning language requires not just learning the facts of a language, but also learning how to use that language to communicate. One common test environment for language use is referential communication, the ability to give a description so that an interlocuter can pick out a referent (object, picture, idea) from a set of possibilities. Adults show sensitivity to both the visual context and their audience during referential communication, calibrating the type of description and the amount of information they provide to their beliefs about the interlocuters knowledge state.

One particular skill in referential communication is the ability to build up a new shared name for an object that initially does not have a canonical name, such as an abstract shape. This ability is tested in *iterated reference games* where a describer identifies abstract shapes from an array of images repeatedly to the same partner. Over repetition, features of the initial verbose descriptions are conventionalized as each pair comes to agree on a shared understanding of how to label each image. Success at this task requires mastery of a number of linguistic and communicative skills: the ability to produce initial descriptions of abstract shapes, monitoring for comprehension and asking for clarification, and appropriately using the shared conversation history to inform referring expressions in later rounds. (TODO any other skills we want to call out?)

All of these are skills that children must learn as part of their acquisition of language. There's been debate on the relative order of different linguistic competencies, with some arguing that pragmatics and tailoring language to accomplish goals is a late addition, and others arguing that sensitivity to communicative intent is an early-arising tool that helps children acquire words. How well do young children do at creating appropriate referential descriptions in an iterated reference game? what's the developmental trajectory of producing expressions to achieve joint understanding? TODO fix

An study on children's referential communication declared young (AGE) children incapable of the task of child-child referential communication (CITATION). In their paradigm, one child was given blocks in a specific order from a dispenser. Their task was to describe the drawing on the block so their their partner could pick out the corresponding block from an unordered set of 6 blocks. Then each child would put their block on a peg, and repeat, until they had stacked all 6 blocks. Children recieved feedback (?) and then played the game repeatedly with the same sets of blocks. When the drawings on the blocks were recognizable farm animals, children as young as TODO were successful. However, when the drawings were abstract shapes, children were not able to produce descriptions. TODO describe what the trajectory was as children got older: In similar experiments with older children, CITE found a gradual slope of improvement with TODO whatever. CITE attributed young children's failures to the children’s use of idiosyncratic referring expressions unique to their own experiences, making it difficult for the pair to converge on shared descriptions. The researchers thus declare children converse in a manner that is too egocentric to accommodate the cooperation required of referential communication. However, the complexity of the stacking paradigm and the large number of potential targets makes this a poor test of children's ability to produce adequate referent expressions as the task demands could tax children's limited executive function and mask children's abilities.

TODO need to figure out which exactly to cite for what of: Krauss & Glucksberg 1977 ; Glucksberg et al 1966 ; Glucksberg & Krauss 1967; Krauss & Glucksberg 1969

Since then, a number of studies have targeted specific skills needed for referential communication, including expectations around consistent labeling ("conversational pacts"), awareness of other's perspectives, and sensitivity to descriptive adequacy in varying contexts. These skills are intertwined, but studies targeting each of them suggest that children show the roots of understanding during the preschool years, albeit expressed inconsistently, and often in non-adultlike ways. HAHA maybe this just isn't true for near/far context stuff and they're just bad at it

One piece of cooperative communication is the expectation that one person will re-use a description that worked before, and not imposing this expectation on other people who were not present. As listeners, preschoolers (3-5 year olds) show an expectation that the same term will be repeated as they are faster to select a target when it is referred to in a consistent way CITATIONS. However, this preference for familiar descriptions is applied regardless of whether they are said by the same person or a new person. Preschoolers are said to be "hyperconventional", often verbally protesting the use of a new term ("That's a horse, not a pony!"). As the producers of descriptions, children show some partner-specificity, but are far from consistent. TODO Koyman et al had 4 and 6 year old children do a version of the paradigm from Brennan & Clark 1996. In a near referring context of different shoes, children used specific referring expressions ("woman's shoe") with one partner. The question was in later trials, when only one shoe was present in the context, would children keep the entrained term or switch back to a more general term ("shoe"). Both 4 and 6 year olds did some of each, but 6 year olds were somewhat more likely to continue using the specific term with the same partner than with a new partner, whereas 4 year olds used expressions at the same rate regardless of partner.

Expectations of consistency are entwined with knowing who knows what and being able to take the perspective of an interlocuter. Young children are notoriously ego-centric (Epley & Morewedge, ), but even preschoolers are able to take other's perspectives, especially when the are not under too much cognitive load (Juan, Khu, Graham). Across the 2-4 year olds range, children are developing sensitivity to what is given their interlocuter based on the discourse history and visual context available to their interlocuter (Matthews 2006). Older preschoolers are more likely to use more given forms such as pronouns when their interlocuter has more context and indefinite forms when their interlocuter has less context. 5-year-old children can also account for privileged ground as they gaze for shorter periods at objects they know their interlocutor cannot view in a retrieval task. (Nilsen, Graham) An ability to overcome the egocentrism is linked to greater levels of executive functioning as measured independently. 
 5 and 6-year-old children show sensitivity to their adult partner’s perspective in the privileged ground when tasked to help them choose objects of varying sizes while some are occluded to their interlocutor. (Nadig, Seviy).

Another skill children need to tailoring the specificity of their utterances to the context. Children struggle with this, with 4 year olds showing some improvement after getting specific feedback that models appropriate descriptions, but still a lot of inconsistency (CITE Matthews 2012) TODO CITE LEUNG STUDY 3 as well When children must pick out one of two very similar images, 4 and 5 year olds aren't good at mentioning the relevant features, although they do better when playing in an interactive game than when not. This suggests that understanding the task and having the task be more similar to children's everyday experiences may be important. 
- Grigoroglou & Papafragou (2019) 
(Morisseau, Davies, Matthews) find that 3 and 5-year-old children can accurately discriminate descriptions that are ambiguous or overly informative by lengthening their response times and asking for clarification when trying to match an expression to two similar images. This discrimination increases in age as 5-year-olds are more sensitive to differences in ambiguity. Children also show an awareness of the information their listeners need by differing their expressions when the situation demands it, as they use longer, complex descriptors when presented with two similar referents, and more vague descriptors when presented with dissimilar ones (Nadig Sedivy).

In addition to testing these 3 skills mentioned above, iterated reference games also pose a couple additional challenges. Producing descriptions is harder since there are not canonical names for the target objects or their features. Additionally, depending on the set up of the game and the number of options, children's limited cognitive resources may impair their performance. A common thread between many studies in referential expression production is that children perform better when the cognitive load of the task is reduced, i.e. fewer distractor referents. (Abbot-Smith, Nursoo, Croll). This suggests that tailored referential expression production is possible in children, but it is likely to be masked in situations that involve cognitive load. TODO not sure where to mention but somewhere we need to address that iterated ref games have the abstract referent thing, so producing a description is less trivial (not just choosing from a set)

TODO Since CITE FOOBAR, only a few studies have revisited the question of how well children can put together different skills to communicate in an iterated reference game. CITE Branigan 2016 tested 72 8-10 year olds on iterated referential communication using a paradigm based on CITE Wilkes-Gibbes & Clark 1992. In the training period, pairs of children matched tangrams in order from a pool of 8 images. Qualitatively, children on average showed the classic patterns of increasing accuracy, increasing speed, and shorter descriptions across repetitions. However, children's level of accuracy was far below what is typical for adults and varied dramatically from pair to pair.

Some of the skills required in iterated reference games are communicative rather than purely linguistic. In CITE BOhn 2019, 4 and 6 year olds communicated target images from a pool of 5 images via a video link (no audio). Children's comprehension was good and increased over repetitions, and children showed signs of agreeing on conventionalized gestures with the partner tending to use the same gestures back when roles switched. Conventionalization was stronger for 6 year olds than 4 year olds, based on the rating of the similarity of gestures within a dyad versus gestures between dyads.

A recent study on younger children examines children's abilities to play an iterated reference game with a parent. CITE LEUNG had TODO child pairs of 4, 6, 8 year olds play a matching game with their parent. Each participant had a tablet that showed two images. The describer had a box around one image and their job was to pick out that image for the other participant. TODO describe this study better! Overall, there were a total of 10 target images, and the images repeated 4 times. In this task, even 4 year olds had an accuracy of TODO and showed ? an increase over repetitions.

Given the potential for task demands in the TODO study and the level of success young children had with their parents at a simplified, less demanding paradigm, we revisit the question of children's ability to converge on appropriate referential expressions with each other.
In the present study, we re-examine young children's ability to establish effective referring expressions with each other in an iterated reference game using a simplified paradigm to reduce cognitive demands.

```{r interface, fig.env = "figure*", fig.pos = "t!", out.width="\\textwidth", fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "Experimental Setup and Procedure. Panel A shows the experimental setup with the teller and guesser across the table from each other. Panel B shows the 4 possible targets; names for targets are for cross-reference with later figures only. Panel C shows the procedure for Experiment 1; within in critical block targets were ordered randomly. Panel D shows the procedure for Experiment 2. \\label{game}", cache=FALSE}

knitr::include_graphics("diagram.pdf")

# edit diagram at 
# https://docs.google.com/drawings/d/1gio1CNSedECJGrkrNDUi_AydPZcYzESfl4WhZD2l9Bc/edit?usp=sharing
```

@@

## Materials
For the target stimuli, we used four of the ten tangram images from @leung, chosen based on visual dissimilarity (Figure \ref{game}B). We coded the matching game using Empirica and hosted it on a lab server (CITATION). We then accessed the game on the web on tablets that were locked in a kiosk mode so children could not navigate to other websites or applications during the game.

## Procedure
Once a pair of children agreed to play the game, a research assistant took them to a quiet testing room where the game was explained to them. Children were introduced to a stuffed animal "Smurfy" who wanted to play a matching game. Children sat across a table from each other, each with a tablet in front of them (Figure \ref{game}A). On each trial, one child saw two images, one of them in a black box, and was asked to "say what they saw" in the black box so their partner (and Smurfy) could tap the corresponding image. The guesser saw the same two images (in a randomized order), but with neither boxed. Upon tapping an image, both children received feedback in form of a smiley or frowny face and an audible sound. After each trial, children's roles switched. Children passed Smurfy back and forth to help them keep track of whether they were the "guesser" or "teller" on a given trial.

Children completed two warm-up trials with black and white images of familiar shapes, followed by 3 blocks of the 4 targets (Figure \ref{game}C). Targets were randomly paired with another of the critical images as the foil.

@@

@@

## Materials
The same 4 critical images were used as in experiment 1, although this time, children saw these images 4 times. In response to some children struggling with the abrupt switch from nameable to non-nameable shapes, we introduced more practice trials for experiment 2. We used a total of 4 practice trials, designed to transition from easily recognizable shapes to slightly blockier black and wide shapes to smooth the transition to the critical trials.

## Procedure
The procedure was much the same (Figure \ref{game}D). We added an initial "bubble popping" exercise to give children practice with how to tap the tablet appropriately (this was an issue for some children in the first experiment). The smurfy puppet was swapped out for a more attractive smurfy stuffed animal. The experimental script was fully written out so children all received the same instructions. To prevent experimenter's influencing children's descriptions or understanding of descriptions, we wrote up contingency statements that the experimenter could use to prompt children who were not giving descriptions or making selections. TODO link to materials for where the script is. The idea was that the experimenter would help with understanding of game mechanics such as who's turn it was to tell and who should press the screen to move the game along if children stalled, but would not provide or repeat any content about the images, what to ask, or whether a description was adequate.
